Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-12 WRITEUP/ms.tex
add zoom in plot

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_3by1_0}.png}
\caption{
Toomre $Q$ maps derived from the gas (left) and stellar (middle) components, respectively. 
A map of the effective two-component Toomre $Q_{\rm eff}$ parameter is shown in the right panel. 
All maps are projected onto the $xy$-plane.
Positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
% Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
A smoothing length of 30\,pc has been applied to the maps.
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ 
are likely gravitationally unstable.
\label{fig:Qeff}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.92\textwidth]{\figpath/{ss16_toomre_combined_3by1_0}.png}
\includegraphics[trim=0 0 0 65, clip, width=0.95\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_0.8}.png}
\caption{
Toomre $Q$ maps derived from the 
central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
Gas-only $Q$ are shown in the left panels and stellar-only $Q$ are shown in the middle panels.
Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels. 
All maps are projected onto the $xy$-plane.
Positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
A smoothing length of 30\,pc has been applied to the maps.
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q}$\eq0.
Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ 
are likely gravitationally unstable.
\label{fig:Qeff}}
\end{figure*}
